DPSh: Automated Data-Parallel Processing in the Shell

### 2020-03-30 pldi/draft.tex
Add some notes in the distributability DSL section

\paragraph{Distributability DSL}
The DSL for distributability description (Fig.~\ref{fig:dsl}) is
designed to classify commands into multiple categories
given their options.

@@

%% \paragraph{Pure Commands}
%
\noindent
In addition to the commands in \sta that can be parallelized in a
straightforward way, there also exists a subclass of commands in \pur
that can be parallelized using divide-and-conquer techniques (as
mentioned in \cref{cmd}). In order to support the parallelization of
arbitrary commands in this category, \sys allows command developers to
provide custom map and reduce steps for them, where the map
is in \sta and the reduce in \pur, and their composition produces the
same output with the initial command. \sys can then replace occurrences
of these commands with their map and reduce parts, enabling their
parallelization.

@@

>>>>

\paragraph{Distributability DSL}
The DSL for distributability description (Fig.~\ref{fig:dsl} \kk{I
  think that the language definition should be in a technical report,
  and here we should only give intuition and the \ttt{comm} example})
is designed to classify commands into multiple categories given their
options.

@@

%% \paragraph{Pure Commands}
%
\noindent
In addition to the commands in \sta that can be parallelized in a
straightforward way, there also exists a subclass of commands in \pur
that can be parallelized using divide-and-conquer techniques (as
mentioned in \cref{cmd}). In order to support the parallelization of
arbitrary commands in this category, \sys allows command developers to
provide custom map and reduce steps for them, where the map is in \sta
and the reduce in \pur, and their composition produces the same output
with the initial command. \sys can then replace occurrences of these
commands with their map and reduce parts, enabling their
parallelization. \TODO{Mention that we have done this for several pure
  commands in coreutils, providing the foundation}

@@

\TODO{Talk about the importance of eagerness and why we need to
  enforce it to get benefits. Discuss the necessity of having files as
  buffers and how we addressed the issue of cat's lazy consumption of
  its inputs.}
